Guarded Recursion in Agda via Sized Types

### 2019-01-12 code-oneclock-paper/latex/paper.tex
new symbol for weakenC and weakenT in syntax
Minor additions to text, removed appendix.

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{₃}{$_3$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{∞}{$\infty$}
% Add more as you need them (shouldn't happen often).

@@

Lastly, we use operations on sets and presheaves to define the type operators in simple type theory.
For sets, we use products, sums, and function types in Agda.
Products, sums, and exponentials of presheaves are interpreted with the operations in \Cref{sec:presheaves}.

\section{Modelling Guarded Recursion}
We model something like guarrded ercursion.
Oh, and guarded recursive types

@@

\appendix
\section{Omitted Proofs}

>>>>

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{₃}{$_3$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{β}{$\beta$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{θ}{$\theta$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{∈}{$\in$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{■}{$\blacksquare$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
\newunicodechar{∞}{$\infty$}
\newunicodechar{⇑}{$\Uparrow$}
% Add more as you need them (shouldn't happen often).

@@

Lastly, we use operations on sets and presheaves to define the type operators in simple type theory.
For sets, we use products, sums, and function types in Agda.
Products, sums, and exponentials of presheaves are interpreted with the operations in \Cref{sec:presheaves}.
We only give the notation for function types.

\input{CloTT/TypeFormers/FunctionType}

\section{Modelling Guarded Recursion}
Now we got the simple type formers and their terms.
The next step is add the type formers required for guarded recursion.
We start by defining clock quantification and later, and how to construct terms of those types.
In addition, we define the fixpoint combinator.
We end this section by giving a type former for guarded recursive types.

@@
